---
title: "Gameday package"
author: "Rindra R."
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Gameday package}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---


## Introduction

`gameday` is an awesome R package for NHL fans who wants to check game calendar and scores. 
We'll need to import our new library. 
```{r}
library("gameday")
```


## Installing and loading the package
To install and load the library, run the following: 
```{r, eval= F}
install_github("giocode/gameday")
library(gameday)
```


## Using the gday function

The function `gday()` takes two arguments: an NHL `team` name and a `date`. Then, it returns a Boolean specifying whether the team plays on that date. Default values are provided for these arguments by assuming you are a Canucks fan and you want to know if your favorite team is playing today.
Here are some examples of applications. 
Vancouver is not playing today. 
```{r}
gday()
```
The above is the same when I wrote this vignette): 
```{r}
gday("Canucks", "2014-11-24")
```
However, can see that the Canucks did play yesterday.
```{r}
gday(date = "2014-11-23")
```
Notice how important it was to specify the argument name `date` in the last call since we omitted the `team` argument. 


## Checking the NHL Scores

The `scores` function only takes a `date` as argument. It returns a data.frame representing the scores of all the games on that date. By default, the date is set to today's date when it is not specified.

```{r}
scores()
```

```{r}
scores("2014-11-23")
```

```{r}
scores("2014-11-22")
```

> You need internet connexion when using gameday.
